---
title: "Incorporating flipbooks in learnR tutorials"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggdag)
library(flipbookr)
knitr::opts_chunk$set(echo = FALSE)
```

## Proof of concept: embedding `flipbookr` slides in `learnr` tutorials 
This is a demonstration tutorial illustrating how [`flipbookr` slides](https://evamaerey.github.io/flipbooks/about) can be incorporated into [`learnr` interactive tutorials](https://rstudio.github.io/learnr/). The step-by-step illustration of code using a flipbook combined with the hands-on interactive coding chunk provided by `learnr` offers a powerful learning experience. The code to create this demonstration can be found on GitHub [here](https://github.com/MarkHanly/flipbook-in-learnr). This approach was inspired by a talk on `Xaringan` given by [Emi Tanaka](https://emitanaka.org/).

The material on DAGs comes from a more fully developed tutorial from the [UNSW Masters of Health Data Science](https://cbdrh.med.unsw.edu.au/postgraduate-coursework), delivered by the [Centre for Big Data Resource in Health](https://cbdrh.med.unsw.edu.au/).  

### Coding DAGS in R: Overview 
The DAGs in this tutorial are created using the `ggdag` function. You can read a detailed vignette on the package [here](https://cran.r-project.org/web/packages/ggdag/vignettes/intro-to-ggdag.html).


### Demonstration
Navigate through the slides below to see an example.

```{r, out.width='100%', out.height='100%'}
knitr::include_url("images/flipbook.html")
```

Note that:

* You can fix the node positions using `coords = `. Otherwise they are randomly chosen. 
* The funtion `dagify()` is used to define the relationships between nodes. E.g. `y ~ x` indicates that an arrow will point from **x** to **y**.  
* Passing the output of `dagify()` to `node_parents(x)` creates a dataframe distinguishing between child and parent nodes of **x**. 
* `geom_dag_point()` and `geom_dag_edges()` plot the results. 
* Applying `theme_dag()` provides a nice clean plot. 
 
 
### Try it yourself
Try experimenting with the code below to create your own DAG.

```{r ggdag1, exercise = TRUE, exercise.lines = 25}
# specifying fixed coordinates means that the nodes of the DAG will 
# always be in the same in the same place. If we don't include this, 
# the nodes will be randomly arranged each time the DAG is drawn
coords <- list(
        x = c(x = 0, y = 1, a = 1, b = 0),
        y = c(x = 0, y = 1, a = 0, b = 1)
    )


dagify(y ~ x + a + b,
       x ~ a + b,
       exposure = "x",
       outcome = "y",
       coords = coords) %>%  
  node_parents("x") %>% 
  ggplot(aes(x=x, y=y, xend=xend, yend=yend, color=parent)) + 
  geom_dag_point() + 
  geom_dag_edges() +
  geom_dag_text(col = "white", size = 6) + 
  geom_dag_edges_link(arrow = grid::arrow()) + 
  theme_dag() + 
  scale_color_hue(
    breaks  = c("parent", "child")
    ) 
```
 
You might notice that this code differs slightly from the code in the flipbook slides above. The flipbook code uses _slow ggplot_ as described by the `flipbookr` package developer Evangeline Reynolds in her [blog](https://evangelinereynolds.netlify.app/post/slow-ggplot/). Slow ggplot is an approach to writing ggplot code that focuses on incremental changes, for example, instead of specifying `aes(x=xy, y=y, xend=xend, yend=yend, color=parent)` in a single line, slow ggplot separates out each aesthetic element to a separate line, to emphasise how that element affects the graph. The editable code above dispenses with the slow ggplot syntax, and is more typical of how you will write R code in the wild.    
 
 


