---
title: "Incorporating flipbooks in learnR tutorials"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggdag)
library(flipbookr)
knitr::opts_chunk$set(echo = FALSE)
```

## Coding DAGS in R

### Overview 
The DAGs in this tutorial are created using the `ggdag` function. You can read a detailed vignette on the package [here](https://cran.r-project.org/web/packages/ggdag/vignettes/intro-to-ggdag.html).


### Demonstration
Navigate through the slides below to see an example.

```{r, out.width='100%', out.height='100%'}
knitr::include_url("images/flipbook.html")
```

Note that:

* The funtion `dagify()` is used to define the relationships between nodes. For example `y ~ x` indicates that an arrow will point from **x** to **y**.  
* Passing the output of `dagify()` to `node_parents()` creates a dataframe distinguishing between child and parent nodes. 
* `geom_dag_point()` and `geom_dag_edges()` plot the results. 
* Applying `theme_dag()` provides a nice clean plot. 
 
 
### Try it yourself
Try experimenting with the code below to create your own DAG.

```{r ggdag1, exercise = TRUE, exercise.lines = 30}
coords <- list(
        x = c(x = 0, y = 1, a = 1, b = 0),
        y = c(x = 0, y = 1, a = 0, b = 1)
    )
dagify(y ~ x + a + b,
       x ~ a + b,
       exposure = "x",
       outcome = "y",
       coords = coords) %>%  
  node_parents("x") %>% 
  ggplot() + 
  aes(x = x) +
  aes(y = y) + 
  geom_dag_point() + 
  geom_dag_text(col = "white") + 
  geom_dag_edges() +
  aes(xend = xend) +
  aes(yend = yend) + 
  aes(color = parent) + 
  theme_dag() + 
  scale_color_hue(
    breaks  = c("parent", "child")
    ) 
```
 
 
 


